%-------------------------
% Resume in Latex
% Author : Sreerag PC
% Modified from Jake Gutierrez template
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\LARGE \scshape SREERAG PC} \\ \vspace{1pt}
    Calicut, India $\cdot$ 
    \href{mailto:sreerag939@gmail.com}{sreerag939@gmail.com} $\cdot$ 
    \href{tel:+919048212429}{+91-90482-12429} \\ \vspace{1pt}
    \href{https://github.com/sreeragpc}{\texttt{github.com/sreeragpc}} $\cdot$ 
    \href{https://www.linkedin.com/in/sreeragpc}{\texttt{linkedin.com/in/sreeragpc}} $\cdot$ 
    \href{https://www.sreeragpc.com}{\texttt{sreeragpc.com}} $\cdot$ 
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

% NEW ROLE ADDED HERE
\resumeSubheading
    {{\textbf{CloudEQ}\normalfont \textit{- Chandigarh}}}{}
    {\textbf{Senior DevOps Engineer I}\textit{ - Trimble, Equiniti, and  Redbull}}{ \hfill \textit{Aug 2025 -- Present}}{}
    \resumeItemListStart
      \resumeItem{Implemented new layered module approach for Newrelic Terraform IaC ,which reduces code repeatability upto 80 percentage.}
      \resumeItem{Migrated from ServiceNow to Halo for Redbull for it's newrelic automation pipelines }
    \resumeItemListEnd
  \vspace{-10pt}

\resumeSubheading
    {}{}
    {\textbf{Software Engineer II}\textit{ - Worked for Redbull, Equiniti and American Woodmark}}{ \hfill \textit{Oct 2023 -- Jul 2025}}{}
    \resumeItemListStart
      \resumeItem{Developed and executed an automation solution using PowerCLI and vCenter to install AWS Discovery Agent on 700+ servers, reducing manual effort and deployment time.}
      \resumeItem{Restored operational stability by resolving critical pipeline errors in muting rule automation solutions integrating New Relic with ServiceNow.}
      \resumeItem{Proposed and supported the implementation of a Datadog-based monitoring solution to enhance pipeline visibility and reliability.}
      \resumeItem{Led the planning and execution of data recovery for Red Bull’s storage account, including full restoration of muting rules.}
      \resumeItem{Automated installation and configuration of observability features for 15+ services across multiple servers using Puppet.}
      \resumeItem{Designed and deployed observability dashboards and monitoring alerts using Terraform, integrated with New Relic for real-time insights.}
    \resumeItemListEnd
  \vspace{-15pt} 
  \resumeSubheading
    {}{}
    {\textbf{Software Engineer I}\textit{ - Worked for McDonald's}}{ \hfill \textit{Oct 2022 -- Sept 2023}}{}
    \resumeItemListStart
      \resumeItem{Automated governance for JFrog, GitHub, and SonarQube with security, compliance, and monitoring enhancements.}
      \resumeItem{Orchestrated provisioning of 243 JFrog SaaS repos as part of migration.}
      \resumeItem{Developed automation solutions for enterprise DevOps: compliance, cost, auditing, and alerts.}
    \resumeItemListEnd

\resumeSubheading 
    {{\textbf{Crossroads}\normalfont \textit{- Calicut}}}{}
    {\textbf{ML and Python Backend Trainee} }{\hfill \textit{Feb 2022 -- Oct 2022}}{}
    \resumeItemListStart
      \resumeItem{Worked on Python Django full-stack projects with end-to-end deployment.}
      \resumeItem{Contributed to ML model development and integration.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{HireYourMentor.com} $|$ \emph{Python, Django, PostgreSQL, AWS, Nginx}}{}
      \resumeItemListStart
        \resumeItem{Mentor booking web app with slot scheduling, Twilio SMS, and Razorpay integration.}
        \resumeItem{UI/UX in Figma, database in DrawSQL, deployed using EC2, Nginx, and RDS.}
        \resumeItem{GitHub Repo: \href{https://github.com/sreeragpc/hireyourmentor-aws}{\texttt{Link}} $\cdot$ }
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.30in, label={}]
  \small \item{\textbf{Programming}{: Python, C, PowerShell, Terraform (HCL), Puppet, SQL}} \\
  \small \item{\textbf{DevOps}{: AWS, Azure, Terraform, Git, GitHub, SonarQube, JFrog}} \\
  \small \item{\textbf{Web}{: Django, HTML/CSS, Bootstrap, JQuery, Ajax, PostgreSQL, MySQL}} \\
  \small \item{\textbf{Tools}{: Jupyter, VS Code, EC2, RDS, SQLite, Azure SQL, InfluxDB, MongoDB, NewRelic }} 
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NSS College of Engineering, Palakkad}{2016 -- 2020}
      {B.Tech in Mechanical Engineering}{}
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeSubHeadingListStart
  \resumeItem{AWS Cloud Practitioner}
  \resumeItem{Microsoft Azure Fundamentals (AZ-900)}
  \resumeItem{New Relic Verified Foundation (NVF)}
\resumeSubHeadingListEnd

\end{document}
